---
title: "Homework 2: Linear Regression"
author: "Carly Greutert"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(caret)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(tidymodels)
library(corrplot)
library(ggthemes)
library(cli)
library(recipes)
library(yardstick)
tidymodels_prefer()
```
1. 
```{r}
abalone <- read_csv('C:\\Program Files\\Git\\tmp\\131-hw2\\abalone.csv')
abalone <- abalone %>% 
mutate(age = rings + 1.5)
abalone <- subset(abalone, select = -(rings))
abalone %>% 
ggplot(aes(x = age))+ geom_histogram(bins = 60)
```

Age seems to be normally distributed, although slightly positively skewed, with 11 being roughly the mean age, although it has a few older outliers.
2. 
```{r}
set.seed(1111)
abalone_split <- initial_split(abalone, prop = 0.80, strata = 'age')
abalone_train <- training(abalone_split)
abalone_test <- testing(abalone_split)
```
3.
```{r}
abalone_recipe <- recipe(age ~ ., data = abalone_train)
abalone_recipe <- abalone_recipe %>% 
  step_dummy(all_nominal_predictors())%>%
  step_interact(~contains('type'):shucked_weight) %>%
  step_interact(~longest_shell:diameter)%>%
  step_interact(~shucked_weight:shell_weight)%>% 
  step_center(all_predictors()) %>%
  step_scale(all_predictors())
abalone_recipe
```

You should not use rings to predict age since age is directly derived from the recorded rings, so there is no element of randomness. Furthermore, the goal is to not need to cut open the abalone and count the rings to predict age.                                                     
4.
```{r}
lm_model <- linear_reg() %>% 
  set_engine("lm")
```

5.
```{r}
lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(abalone_recipe)
```
6.
```{r}
lm_fit <- fit(lm_wflow, abalone_train)
fabalone <- data.frame(type = 'F', longest_shell = 0.50, diameter = 0.10, height = 0.30, whole_weight = 4, shucked_weight = 1, viscera_weight = 2, shell_weight = 1)
predict(lm_fit, fabalone)
```
7.
```{r}
abalone_metrics <- metric_set(rmse, rsq, mae)
abalone_train_res <- predict(lm_fit, new_data = abalone_train %>% select(-age))
abalone_train_res <- bind_cols(abalone_train_res, abalone_train %>% select(age))
abalone_train_res %>% head()
abalone_metrics(abalone_train_res, truth = age, 
                estimate = .pred)
```

Our predicted estimates were a little high and the $R^2$ value ended up being 0.563, which is decent, but a different model may be more appropriate.  